\documentclass[11pt]{article}

% --- Packages ---
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}      % For images
\usepackage{booktabs}      % Nicer tables
\usepackage{enumitem}      % Tighter, consistent lists
\usepackage{hyperref}      % Clickable refs/links
\usepackage{microtype}     % Better typography
\usepackage{xcolor}        % Colors for links

% --- Hyperref setup ---
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue,
  citecolor=blue,
  pdfauthor={Bryan Gonzalez, Kalen Hoang Tiana Luu, Janelle Rivera, Christine Vu, Rojina Zalzar},
  pdftitle={Book Exchange Django Application - Development Document}
}

% --- Title Info ---
\title{Book Exchange Django Application\\\large Development Document}
\author{Bryan Gonzalez, Kalen Hoang Tiana Luu, Janelle Rivera, Christine Vu, Rojina Zalzar}
\date{November 5, 2025}

% --- List spacing ---
\setlist{itemsep=0.25em, topsep=0.25em}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Overview}
    The Book Exchange web application facilitates a community-driven platform where users can share, discover, and manage books. The primary audience is students and general users interested in exchanging books in an organized, interactive environment.

\section{App Purpose and Features}

\subsection{Core Functions}
\begin{itemize}
  \item \textbf{Book Listings and Details:} Browse posted books and view details including price, images, posting user, and external links.
  
  \item \textbf{User Registration \& Authentication:} New users can sign up; existing users can sign in to access interactive features.
  
  \item \textbf{Book Management:} Post books to share and manage personal postings.
  
  \item \textbf{Search:} Search for books by name to streamline discovery.
  
  \item \textbf{User-Centric Lists:} Personal views for posted, purchased, and favorited books.
  
\end{itemize}

\subsection{Advanced Interactive Features}
\begin{itemize}
  \item \textbf{Ratings:} Rate books from 1--5 stars. Ratings are anonymous except for the current user’s own rating.
  
  \item \textbf{Favorites:} Add or remove books from a favorites list for quick access.
  
  \item \textbf{Comments:} Add comments on book detail pages; users may delete only their own comments.
  
  \item \textbf{Shopping Cart \& Checkout:} Add books to a cart and check out to mark items as purchased.
  
  \item \textbf{Access Control:} Views such as \emph{My Books} and \emph{Checkout} require login. Unauthorized access shows a friendly ``You need to log in'' message rather than redirecting.
  
\end{itemize}

\subsection{Student Required Features}
\begin{itemize}
  \item \textbf{About Us Page:} A dedicated page describing the app’s purpose and development context.
  
  \item \textbf{Book Search:} Case-insensitive search by name with immediate results.
  
  \item \textbf{Navigation Reformat:} Responsive, user-friendly navigation bar styled with Bootstrap/CSS.
  
\end{itemize}

\subsection{Chosen Additional Features}
\begin{itemize}
  \item \textbf{Message Box (Comments):} Users can add comments to books and manage their own comments.
  
  \item \textbf{Shopping Cart:} Add multiple books and manage purchases easily.
  
  \item \textbf{Ratings:} Star rating system on book detail pages for qualitative feedback.
  
\end{itemize}

\subsection{Key Challenges and Solutions}
\begin{itemize}
  \item \textbf{Login Redirection 404:}
  \emph{Problem:} Access to login-protected pages redirected to a non-existent \texttt{/accounts/login/}, causing 404 errors.\\
  \emph{Solution:} Removed the default \texttt{@login\_required} redirect. Added manual \texttt{request.user.is\_authenticated} checks in views and rendered a custom login-required template.
  
  \item \textbf{Anonymous Ratings Display:}
  \emph{Need:} Show ratings while preserving privacy.\\
  \emph{Solution:} In templates, display ``You'' for the current user’s rating and ``Anonymous'' for others.

  \item \textbf{Favorites Toggle:}
  \emph{Need:} Seamless add/remove without confusion.\\
  \emph{Solution:} Implemented a toggle button with conditional template rendering to switch between ``Add to Favorites'' and ``Remove from Favorites.''

  \item \textbf{Comment Ownership \& Delete Control:}
  \emph{Need:} Ensure users can delete only their own comments.\\
  \emph{Solution:} Server-side authorization check in the delete view, returning \texttt{HttpResponseForbidden} on failure.
  
\end{itemize}

\section{Summary of Implemented Requirements}
\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Requirement} & \textbf{Status} & \textbf{Notes} \\
\midrule
About Us & Completed & Informational page (includes CSULA logo image) \\
Search a Book & Completed & Case-insensitive search by name \\
Reformat Nav & Completed & Bootstrap/CSS responsive navigation bar \\
Message Box (Comments) & Completed & Add/delete with ownership control \\
Shopping Cart & Completed & Add to cart, view cart, checkout \\
Ratings & Completed & 1--5 stars, anonymous display \\
Favorite List & Completed & User-specific favorites with toggle \\
\bottomrule
\end{tabular}
\end{center}

\section{Usage Flow for Users}
\begin{itemize}
  \item Visit the homepage to browse or search books.
  \item Register or log in to access the full feature set.
  \item Post books to share with others.
  \item Add books to the shopping cart and check out.
  \item Rate and comment on books.
  \item Favorite/unfavorite books for quick access.
  \item Manage personal lists (posted, purchased, favorites).
  \item If not logged in, friendly reminder pages clarify when login is required.
  
\end{itemize}

\end{document}
